Performance of Rookie Can Predict Price of Their RC based Prizm Cards

### 2024-04-04 paper/paper.qmd
download data

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Harrison Huang
thanks: "Code and data are available at: LINK."
date: today 
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Performance of Rookie Can Predict Price of Their RC based Prizm Cards"
subtitle: "My subtitle if needed"
author: 
  - Harrison Huang
thanks: "Code and data are available at: LINK."
date: today 
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
